Twisted 11-dimensional supergravity, I

### 2021-09-13 symmetry.tex
merge

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle

\newpage

\section{A family of moduli spaces} 
\label{s:dfn}

In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.

\subsection{Divergence-free vector fields}

\subsubsection{}
\label{sec:divfree}
We set up some notations and conventions in the context of complex geometry. 
Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
\]
This is a free resolution for the sheaf of holomorphic sections of $V$.

Suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
The divergence $\div(\mu)$ of a holomorphic vector field $\mu$ is defined by the formula
\[
\div (\mu) \wedge \Omega = L_\mu (\Omega)
\]
where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.

Let $\T_X$ denote the holomorphic tangent bundle and consider its Dolbeault complex $\Omega^{0,\bu}(X , \T_X)$ resolving the sheaf of holomorphic vector fields. 
The divergence operator extends to the Dolbeault complex to yield a map of cochain complexes 
\[
\div \colon \Omega^{0,\bu}(X , \T_X) \to \Omega^{0,\bu}(X) .
\]

The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
In fact, we can form the complex 
\beqn\label{eqn:cplx1}
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
\end{tikzcd}
\eeqn
The $\dbar$ operator, as always, is left implicit. 
By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.

There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
The Lie bracket defined by the formulas
\begin{align*}
[\mu, \mu'] & = L_\mu \mu' \\
[\mu, \nu] & = L_\mu \nu 
\end{align*}
is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.

The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.

\parsec[sec:Linfty]

Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$. 
The Chevalley--Eilenberg cochain complex is 
\[
\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
\]
The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.

An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
\deq{
  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
}
between their respective Lie algebra cochains. It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.

$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
\deq[eq:newbase]{
%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
}
This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.

The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).

%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.

%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
\brian{coefficients}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
%The linear term $\Psi^{(1)} = \id$ is the identity map. 
%The higher terms $\Psi^{(n)}$ are defined by 
%\brian{someone check me}
%\begin{align*}
%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
%\end{align*}

\parsec
There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}

\subsection{Theories of BF type}

\parsec
Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
\begin{align*}
[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
\end{align*}

We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$. 
The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_S)$ where $L$ is any smooth manifold.

We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.

\subsubsection{}

Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
We recall the construction. 
Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
\[
\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
\]

The fields of the associated BV theory are pairs
\[
  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
\]
Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.

The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.

We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.

\parsec
For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
In both cases, the space of fields equipped with the linear BRST operator is
\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    -n & -n + 1 & -1 & 0 \\ \hline
    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
\end{tikzcd}
\end{equation}
We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.

The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
\deq{
  n = \dim_\C(X) + \dim_\R(L) - 1.
}

We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.

Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
\deq{
  S_0 =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
}
As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.

The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is non polynomial.
\brian{I think the phrasing ``infinite order'' can mean a lot of different things. I've changed it to ``non polynomial''.} 
(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
Explicitly, this action functional is
\deq{
  S_\infty =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
}

We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent. As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
Explicitly, the automorphism is
\begin{multline}
  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
\end{multline}

\subsection{A family of deformations}

\parsec
%check CME
We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type. That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.

Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
\deq{
  \{S + g J, S + g J \} = 0.
}
Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
\deq[eq:2cond]{
  \{S,J\} = \{J,J\} = 0.
}
\begin{thm}
  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above. The local functional 
  \deq{
    J = \gamma (\del \gamma)^k,
  }
  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
\end{thm}
\begin{proof}
  First off, we consider grading issues. In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$. The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$. As such, we have
  \deq{
    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
  }
  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.

  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}. It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field. It remains to check that $\{I_\infty,J\} = 0$. For the quadratic term, we note that 
  \deq{
    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
  }
  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
  \deq{
    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
}
This expression is zero for symmetry reasons. Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form. We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form  
\end{proof}

\subsection{Global symmetry algebra}

\subsection{Further equivalences}

\subsection{Equations of motion}

%whatever we can say about the formal moduli space

\subsection{Boundary conditions}

%foreshadow the Horava--Witten picture

\subsection{One-loop quantization}

%cite result on thf quantization.

\section{Symmetries of the 11-dimensional theory}

\subsection{Component fields}

%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.

@@

@@

Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.

The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.

@@

The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
\begin{align*}
[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
\end{align*}
\end{prop}

@@

As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.

\begin{prop}
\label{prop:gmodel}
Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
\[
H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
\]
Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
The nontrivial Lie brackets are
\begin{align*}
[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
\end{align*}
There is an $L_\infty$ map 
\[
\fg \rightsquigarrow \m2^Q
\] 
which is a quasi-isomorphism of complexes.  
\end{prop}
\begin{proof}
The supercharge $Q$ is odd and of cohomological degree zero.
Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.

@@

\parsec[s:residual]
Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.

\begin{prop}
There is a map of $\ZZ/2$-graded dg Lie algebras 
\[
\fg \to \cL 
\]
where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
\end{prop}
\begin{proof}
Recall the model $\fg$ takes the following form
\beqn 
\begin{tikzcd}
\ul{even} & \ul{odd} & \ul{even} \\
 L_a & \wedge^2 L_b & L^\vee \\
\wedge^2 L_a & & \\
\lie{sl}(5) \\
L_b \ar[r, "\id"] & L_c .
\end{tikzcd}
\eeqn
The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.

The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
\begin{align*}
 L_a & \mapsto 0 \\
 \wedge^2 L_a & \mapsto 0 \\
z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
\end{align*}
One immediately verifies that this is a map of dg Lie algebras. 
\end{proof}

@@

\subsection{Global symmetry algebra}

We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.

To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
It is this dense sub super Lie algebra which is simple.

\begin{thm}\label{thm:global}
Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$. 
\end{thm}

>>>>

\section{Symmetries of the 11-dimensional theory}
\label{sec:symmetry}

\subsection{Global symmetry algebra}
\label{sec:global}

Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
This is encoded by the full BV action of the 11-dimensional theory.
We describe a simpler (strict) super Lie algebra structure present in the cohomology of the space of fields.

In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
More generally, the full cohomology of a $\ZZ/2$ graded space of states with respect to the linear BRST operator results in a super Lie algebra. 
We will refer to this as the global symmetry algebra of the theory.

The main result of this section is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional simple super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.

We recall the definition of this exceptional simple super Lie algebra.
Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.

More precisely, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
It is this dense sub super Lie algebra which is simple.

\begin{thm}\label{thm:global}
Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a one-dimensional central extension of the super Lie algebra $E^{hol}(5,10)$ defined by the even cocycle
\begin{align*}
E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to \CC \\
(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
\end{align*} 
\end{thm}

The parity of the functional in the theorem is odd, but it is also trilinear. 
Thus, as a cocycle in the Chevalley--Eilenberg complex of $E^{hol}(5,10)$ it is of total even parity.

If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cL = \cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
In the $\ZZ/2$ graded world, the parity shifted object $\cL = \Pi \cE$ has the structure of a super $L_\infty$ algebra.

The full BRST operator is given by the BV bracket with the BV action. 
For us, this~is 
\[
\delta = \{S_{BF,\infty} + J, -\} .
\]
The linear BRST operator comes only from the quadratic summands in $S_{BF,\infty}$ and is of the form
\beqn\label{eqn:linearBRST}
\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma} .
\eeqn
The cohomology with respect to $\delta^{(1)}$ is what we referred to above as the global symmetry algebra.
To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$.

On $\CC^5 \times \RR$ the cohomology with respect to the linearized BRST operator $\delta^{(1)}$ consists of the space of triples $(\mu, [\gamma], b)$ where:
\begin{itemize}
\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
\[
\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
\]
Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
\[
[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
\]
\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
This element is also a ghost in the $\ZZ/2$-graded theory. 
\end{itemize}

After parity shifting, we've identified the solutions to the linear equations of motion with triples
\[
(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \CC .
\]
The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
The elements $b$ are central.

The final term in the BV action $\int \gamma \wedge \del \gamma \wedge \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
\beqn\label{eqn:eqb}
\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
\eeqn
Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.

@@

In this section we consider the minimal twist of 11-dimensinoal supersymmetry explicitly. 
We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
In order for this to be a symmetry of the 11-dimensional theory that we proposed in Section \ref{sec:dfn} it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.

@@

Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the M5 brane.
We begin by describing a dg Lie algebra model for the $M2$ brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.

The $M2$ brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.

@@

The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given by the extension of ${\rm Stab}(Q)$ together with the brackets
\begin{align*}
[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
\end{align*}
\end{prop}

@@

As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to the 11-dimensional theory. 
This lemma implies Proposition \ref{prop:model}.

\begin{lem}
\label{lem:gmodel}
Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
\[
H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
\]
Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
The nontrivial Lie brackets are
\begin{align*}
[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
\end{align*}
There is an $L_\infty$ map 
\[
\fg \rightsquigarrow \m2^Q
\] 
which is a quasi-isomorphism of cochain complexes.  
\end{lem}
\begin{proof}
The supercharge $Q$ is odd and of cohomological degree zero.
Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.

@@

\parsec[s:residual]
Consider now the super $L_\infty$ algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.

\begin{prop}
There is a linear map of super $L_\infty$ algebras 
\[
\fg \to \cL 
\]
where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
\end{prop}
\begin{proof}
Recall the model $\fg$ takes the following form
\beqn 
\begin{tikzcd}
\ul{even} & \ul{odd} & \ul{even} \\
 L_1 & \wedge^2 L_2 & L^\vee \\
\wedge^2 L_1 & & \\
\lie{sl}(5) \\
L_2 \ar[r, "\id"] & L_3 \\ 
\CC_c & .
\end{tikzcd}
\eeqn
The subscripts in $L_1, L_2, L_3$ are used to distinguish between the various copies of $L$.

The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
\begin{align*}
 L_1 & \mapsto 0 \\
 \wedge^2 L_1 & \mapsto 0 \\
z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
c \in \CC_c & \mapsto c \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
\end{align*}

It is immediate to check that this is a map of cochain complexes where one equips $\cL$ with the linear BRST differential \eqref{eqn:linearBRST}.
Since $\nu$ does not appear in the image of this map, to check that the higher Lie brackets are preserved one only needs to check that the $2$-ary bracket is preserved and this is immediate. 
\end{proof}

Because this map preserves differentials, it descends to a map in cohomology. 
We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$, it is the trivial one-dimensional central extension of $E (5,10)$. 
The cohomology of $\fg$ is described in Proposition \ref{prop:model}. 
The map
\[
L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC_c \to E (5,10) \oplus \CC_{c'}
\]
is defined by very similar formulas as above
\begin{align*}
 L_1 & \mapsto 0 \\
 \wedge^2 L_1 & \mapsto 0 \\
z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \d z_i \wedge \d z_j \in \Omega^{2}_{cl} (\CC^5) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \Vect_0(\CC^5) \\ \frac{\partial}{\partial z_j} \in L^\vee & \mapsto
\frac{\partial}{\partial z_i} \in \Vect_0(\CC^5) \\
c \in \CC_c & \mapsto c \in \CC_{c'} .
\end{align*}

@@
